Meta RL analyses

### 2018-10-19 meta_RL_analyses.Rmd
Bugfix and new results

```{r}
num_runs = 1
results_dir = "results/results_no_hints_2/"

@@

```{r}
avg_meta_d = meta_d %>%
  group_by(run, meta_task, is_new) %>%
  summarize(avg_reward = mean(reward)) %>%
  group_by(meta_task, is_new) %>%
  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward)) %>%

>>>>

```{r}
num_runs = 1
results_dir = "results/results_h128/"

@@

```{r}
avg_meta_d = meta_d %>%
  group_by(run, meta_task, is_new) %>%
  summarize(avg_reward = mean(reward)) %>%
  group_by(meta_task, is_new) %>%
  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward))
